Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis

### 2019-09-01 03_Preliminary_analysis.Rmd
Tidy up chunks for knitting to function and make html document

```{r PA_Libraries}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
#source("./getPPD2.R")

@@

levels(as.factor(PM_MB_means$Fungicide))
# plot table as a box plot
PM_MB_means %>%
   filter(Fungicide == c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" , "Amistar","Tebeconazole","propiconazole"))%>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   geom_boxplot()+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 30, hjust =.51, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

@@

```{r Fungicide_x_nSprays}
PM_MB_means %>%
   group_by(Fungicide, total_Fungicide) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

@@

How many trials contain all of the most studied fungicides
```{r}
Tebe_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole",]$Trial_ref)
Propi_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "propiconazole",]$Trial_ref)
Amistar_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Amistar",]$Trial_ref)

@@

```{r}

@@

```{r}
# removing 2017 and control data
# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
PM_MB_means1 <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   filter(Year != 2017) %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))

>>>>

```{r PA_Libraries, include=FALSE}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
#source("./getPPD2.R")

@@

# plot table as a box plot
PM_MB_means %>%
   filter(Fungicide == c("200 g/l  Tebuconazole + 120 g/l  Azoxystrobin" , "Amistar","Tebeconazole","propiconazole"))%>%
ggplot(aes(y = prop_YG, x = Fungicide))+
   geom_boxplot()+
   geom_hline(aes(yintercept = 0), size =0.5)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nFungicide type")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Fungicide"))+
   coord_cartesian()+
   theme(axis.text.x = element_text(angle = 30, hjust =.51, vjust = 0.3))
   #scale_x_continuous(limits = c(-0.3,0.6))

@@

```{r Fungicide_x_nSprays, message=FALSE}
PM_MB_means %>%
   group_by(Fungicide, total_Fungicide) %>%
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

@@

How many trials contain all of the most studied fungicides
```{r Trials_with_top_three_Fungicides}
Tebe_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Tebeconazole",]$Trial_ref)
Propi_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "propiconazole",]$Trial_ref)
Amistar_trials <- unique(PM_MB_means[PM_MB_means$Fungicide == "Amistar",]$Trial_ref)

@@

```{r Calculate_cuts, echo=FALSE}
# removing 2017 and control data
# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
PM_MB_means1 <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))

```{r Sulphur_efficacy, echo=FALSE}

@@
